\chapter{Blueprint}

This blueprint tracks the formalization strategy for busy beaver results in Lean 4.
The long-term objective is to combine executable deciders with machine-checked
correctness proofs to derive trustworthy busy beaver bounds.

\section{Project Objectives}

The project is organized around four proof layers:

\begin{itemize}
  \item core Turing machine semantics and indexing,
  \item reachability and finite execution infrastructure,
  \item non-halting criteria and decider soundness,
  \item verified enumeration and implementation equivalence.
\end{itemize}

\section{Formalization Map}

\subsection{Core Semantics}

Main files:
\begin{itemize}
  \item \texttt{Busybeaver/Basic.lean}
  \item \texttt{Busybeaver/Reachability.lean}
  \item \texttt{Busybeaver/Partial.lean}
\end{itemize}

Purpose:
\begin{itemize}
  \item define machine/tape/state transition semantics,
  \item provide reusable lemmas for multi-step execution and indexing invariants.
\end{itemize}

\subsection{Non-Halting Framework}

Main file:
\begin{itemize}
  \item \texttt{Busybeaver/ClosedSet.lean}
\end{itemize}

Purpose:
\begin{itemize}
  \item encode closed-set style non-halting arguments,
  \item provide tactic support for practical certificate-oriented proofs.
\end{itemize}

\subsection{Proof-Carrying Deciders}

Main directory:
\begin{itemize}
  \item \texttt{Busybeaver/Deciders}
\end{itemize}

Purpose:
\begin{itemize}
  \item define executable deciders,
  \item prove each decider sound with respect to the abstract semantics.
\end{itemize}

\subsection{Verified Enumeration}

Main files:
\begin{itemize}
  \item \texttt{Busybeaver/Enumerate/Alg.lean}
  \item \texttt{Busybeaver/Enumerate/Impl.lean}
\end{itemize}

Purpose:
\begin{itemize}
  \item specify machine enumeration in tree normal form,
  \item connect implementation-level enumeration to the formal specification.
\end{itemize}

\section{Current Work Plan}

Near-term priorities:
\begin{itemize}
  \item reduce local proof debt in decider modules,
  \item strengthen semantic bridge lemmas used by multiple deciders,
  \item keep executable tooling aligned with proof artifacts.
\end{itemize}

\section{Expected Outputs}

This blueprint is intended to track:
\begin{itemize}
  \item theorem statements and dependency flow,
  \item implementation-to-specification correspondence points,
  \item progress toward machine-checked busy beaver results.
\end{itemize}
